---
title: "Using myRpackage with the FARS dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using myRpackage with the FARS dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myRpackage)
```

**Note**: for any of these functions to work, the FARS data *must* be located in your current
working directory. 

# Loading Data

The \code{fars_read} function accepts a single argument, \code{filename}, which 
is a path to the FARS .csv file. 

This example uses the sample data contained in the package. 

```{r example_1, eval=FALSE}

filename <- system.file("extdata", "accident_2013_sample.csv", package="myRpackage", mustWork=TRUE)
fars_2013 <- fars_read(filename)

```

# Summarizing Data

The \code{fars_summarize_years} function takes a vector of integers years and 
returns the total number of accidents for each month for a given year. 

```{r example_2, eval=FALSE}
fars_summarize_years(c(2013, 2014))
```

# Visualizing the FARS Data on a Map

The \code{fars_map_state} function takes two integer arguments, \code{state} and 
\code{year} for the state number.

```{r example_3, eval=FALSE}
fars_map_state(5, 2014)
```

